\begin{rSection}{WORK EXPERIENCE}

      \quad\textbf{Software Engineer} | \textit{NashTech Vietnam} \hfill January 2023 - Present\\
      \begin{itemize}
            \itemsep 0pt {} \vspace{-1em}

            \item Team Size: 10

            \item Designed and implemented end-to-end modules of micro-services system, optimization,
                  code reviews, and unit testing, as a full-stack developer.

            \item Demonstrated strong collaboration and communication skills as a member of an Agile Scrum team,
                  consistently contributing to on-time deliveries and improved team efficiency.

            \item Accomplished a 40\% reduction in database execution time and a 20\% decrease in API call elapsed time
                  by optimizing stored procedures and queries, significantly improving system performance.

            \item Automated the processing of 10 million+ records by setting up a completed service,
                  generating daily reports for over 40,000 users, enhancing reporting capabilities.

            \item Shortened dashboard and report development effort by 50\% through the design and integration of Power BI visualizations,
                  which help to streamline processes and expand access to essential business insights.

            \item Minimized authentication and request handling issues during peak times by 50\% through migrating the microservices
                  system from .NET Core 3.1 to .NET 8—including essential components like Duende Identity Server and GraphQL.

            \item Secured testing environments by developing a tool that masked sensitive data across multiple tables—handling 40 million+ records at the largest—enabling
                  enhanced data privacy and compliance with data protection regulations.

            \item Technology stack: .NET 8, Microsoft SQL Server, Docker, Kubernetes, Power BI, ReactJS, Redis, RabbitMQ, GraphQL, RESTful API, gRPC, WebSocket.
      \end{itemize}

      \vspace{1em}

      \quad\textbf{Software Engineer Intern} | \textit{NashTech Vietnam} \hfill September 2022 - December 2022\\
      \begin{itemize}
            \itemsep 0pt {} \vspace{-1em}
            \item Delivered a mock project graded 4.5/5.0 by collaborating with a team of 10 members as a Dev team leader.
            \item Completed two months of .NET training with the highest score of 41/50 (20\% higher than the average).
            \item Achieved an acknowledgment of completion of "The Rookies" program with an Excellent grade from NashTech.
            \item Technology stack: .NET 6, Microsoft SQL Server, ReactJS, RESTful API.
      \end{itemize}

      \vspace{1em}

      \quad\textbf{Software Engineer Intern} | \textit{Viettel IDC} \hfill August 2021 - April 2022\\
      \begin{itemize}
            \itemsep 0pt {} \vspace{-1em}
            \item Released two new cloud services by collaborating with dev teams in full Scrum sprints and Development life cycle,
                  including the service's workflow design, implementation, testing, and debugging.
            \item Completed three-month training on .NET Development, SQL Server, system and database design.
            \item Technology stack: .NET Framework, ASP .NET MVC, SQL Server, KnockoutJS, Git.

      \end{itemize}

\end{rSection}


